\textsf{Are large language models superhuman chemists?}

### 2024-03-28 src/tex/sections/manually_sources_table.tex

\hline
NMR spectroscopy & Questions are based on images shared via the Twitter account (https://twitter.com/NMRspectroscopy). & 5 \\
\hline
Analytical chemistry & Questions are based on exercises in master student examination at the Friedrich Schiller University, Jena, Germany. & 22 \\
\hline
\multirow{2}{*}{General chemistry} & Questions originate from examinations for grade 10 at the Marist Comprenhensive Academy Uturu, Nigeria. & 6 \\
 & Questions originate from the Bachelor of Science courses  at the Technical University of Munich, Germany. & 8 \\
 \hline
\begin{tabular}[c]{@{}l@{}}Functional materials and \\ nanomaterials\end{tabular} & Questions are based on exercises in a seminar conducted at the Friedrich Schiller University, Jena, Germany. & 8 \\
\hline
Combustion engineering & Based on a Master of Science examination paper at the University of Magdeburg, Germany & 1 \\
\hline
Materials' synthesis & Questions are based on seminars on material synthesis from Friedrich Schiller University, Jena, Germany. & 11 \\

\hline
Chemistry olympiad & National and International Olympiads held in US, UK and Moldova & 193 \\
Organic reactivity & Based on Bachelor of Science in Chemistry at the Technical University of Munich, Germany & 34 \\
\hline
Periodic table & Manually created & 15 \\
\hline
Polymer chemistry & Based on examinations at the University of Hamburg, Germany & 17 \\
\hline
Textbook questions & Various textbooks covering biomolecular science, drug synthesis, molecular structure, organic chemistry, and X-ray crystallography. & 202 \\
\hline
\multirow{1}{*}{Safety} &
 Based on the question bank published by the Federal/State Working Group  on Chemical Safety (BLAC), which is used for the expertise examination (“Sachkundeprufung”) & 90 \\
\hline
\end{tabular}
\end{table}

>>>>

\hline
NMR spectroscopy & Questions are based on images shared via the Twitter account (https://twitter.com/NMRspectroscopy). & 5 \\
\hline
Analytical chemistry & Questions are based on exercises in master student examination at the Friedrich Schiller University, Jena, Germany. &  \variable{output/question_count_per_dir/json_file_counts_analytical_chemistry.txt} \\
\hline
\multirow{2}{*}{General chemistry} & Questions originate from examinations for grade 10 at the Marist Comprenhensive Academy Uturu, Nigeria. & \variable{output/question_count_per_dir/json_file_counts_Gen_Chem_MCA.txt} \\
 & Questions originate from the Bachelor of Science courses  at the Technical University of Munich, Germany. & 8 \\
 \hline
\begin{tabular}[c]{@{}l@{}}Functional materials and \\ nanomaterials\end{tabular} & Questions are based on exercises in a seminar conducted at the Friedrich Schiller University, Jena, Germany. & \variable{output/question_count_per_dir/json_file_counts_func_mats_and_nanomats.txt} \\
\hline
Combustion engineering & Based on a Master of Science examination paper at the University of Magdeburg, Germany & \variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} \\
\hline
Materials' synthesis & Questions are based on seminars on material synthesis from Friedrich Schiller University, Jena, Germany. & \variable{output/question_count_per_dir/json_file_counts_materials_synthesis.txt} \\
\hline
Chemistry olympiad & National and International Olympiads held in US, UK and Moldova & \variable{output/question_count_per_dir/json_file_counts_icho.txt} \\
Organic reactivity & Based on Bachelor of Science in Chemistry at the Technical University of Munich, Germany & \variable{output/question_count_per_dir/json_file_counts_organic_reactivity.txt} \\
\hline
Periodic table & Manually created & \variable{output/question_count_per_dir/json_file_counts_periodic_table_properties.txt} \\
\hline
Polymer chemistry & Based on examinations at the University of Hamburg, Germany & \variable{output/question_count_per_dir/json_file_counts_polymer_chemistry.txt} \\
\hline
Textbook questions & Various textbooks covering biomolecular science, drug synthesis, molecular structure, organic chemistry, and X-ray crystallography. & \variable{output/question_count_per_dir/json_file_counts_oup.txt} \\
\hline
\multirow{1}{*}{Safety} &
 Based on the question bank published by the Federal/State Working Group  on Chemical Safety (BLAC), which is used for the expertise examination (“Sachkundeprufung”) & \variable{output/question_count_per_dir/json_file_counts_blac_gfk.txt} \\
\hline
\end{tabular}
\end{table}
